Example output from simulations for MBNL1 where Va = 0

### 2020-01-28 null_replication/scripts/mbnl1_analysis.rmd
upd

```{r}
ped <- fread("temp.raw", he=T)
fam <- fread("../data/scratch/MBNL1_rs67903230_rs13069559/18778_disc.fam")
mat <- ped[,-c(1:6)] %>% as.data.frame()

@@

>>>>

```{r}
ped <- fread("temp.raw", he=T)
fam <- fread("../data/scratch/MBNL1_rs67903230_rs13069559/18778_disc.fam")
mat <- ped[,-c(1:6)] %>% as.data.frame()
```

Allele frequency of rs13069559:

```{r}
sum(mat[,1], na.rm=T) / (2 * sum(!is.na(mat[,1])))
```

```{r}

@@

## Restricting tests based on minimum cell count

Find pairs where minimum cell number is 5 or more, as was used in the original paper

```{r}
getcells <- function(mincount)
{
	cells <- mclapply(2:ncol(mat), function(x)
	{
		tab <- table(mat[,1], mat[,x])
		return(length(tab) == 9 & min(tab) >= mincount)
	}, mc.cores=16)

	cells <- unlist(cells)
	return(cells)
}

cells5 <- getcells(5)
cells3 <- getcells(3)
table(cells5)
table(cells3)
```

So, this drastically reduces the number of variants remaining in the analysis

```{r}
estlambda <- function(fval)
{
	median(fval) / qchisq(0.5, 4) * 4
}

estlambda(b$fast_f4)
estlambda(b$r_f4)
estlambda(b$fast_f4[cells3])
estlambda(b$r_f4[cells3])
estlambda(b$fast_f4[cells5])
estlambda(b$r_f4[cells5])
```
